\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-23 trunk/arch.tex
Few additions in regard to Javier comments

\item \emph{Coupling} a tighter integration between the planning
  process and world evolution to ensure that planning occurs
  \emph{during continuous} state update. By doing so, the planner is
  better informed in its deliberation despite a larger latency than
  the changing world.

@@

@@

\item Integrate the external state as provided by the owner of each
  external timeline into the plan database.

@@

A key aspect of the \rx framework is interleaved plan execution. As
noted above, it is synchronization which drives planning, so the
co-mingling between these two processes is critical to maintaining
state within a robot especially when it is immersed in a dynamic
environment. Further, it is important that \rx maintain
% A core aspect of this reactor is that it takes advantage of the
% specific sequencing enforced by the \rx architecture along with the
% fact that only 
one $plan$ structure shared between synchronization and planning. This
allows these two processes to not only be interleaved for agent
responsiveness, but ensures a viable mechanism to communicate.

>>>>

\item \emph{Coupling} a tighter integration between the planning
  process and world evolution to ensure that planning occurs
  \emph{during continuous} state update in the {\em same} polan
  database used for planning. By doing so, the planner is
  better informed in its deliberation despite a larger latency than
  the changing world. 
\end{itemize}

@@

It is important to note that in T-REX architecture the only critical
task of a reactor is to sucessfully identify its state through
synchronization as the execution frontier advances. Indeed, a reactor
that fails to integrate its {\em external} state updates and/or
identify its {\em internal} state at any tick express that it is not
able anymore to explain the state of the world. In the agent point of
view that means that any state information from this reactor is not to
be trucsted anymore and will result on this reactor exclusion from the
execution cycle. As the agent destroy the  faulty reactor is
destraoyed the agent produced on all of its former {\em internal}
timelines the special observation \texttt{Failed} to all the reactors
which did declare these state variables as {\em external} informing
them through this that this sepcific state varaiable is currently
unavailable. On the other hand all goals exchanged between reactors
are considered as rejectable by the reactor that manages them. As a
result the falure to find a plwn for these goals, while to be avoided,
is not considered as a critical failure of the reactor and will only
result on these goals being ignored until new goals are received.

Take for example our AUV agent from Fig. \ref{fig:agent},
and assume that the \texttt{Sampling} reactor failed to synchronize;
in  such case this reactor is destroyed and both
\texttt{Sampling\_policy} and \texttt{Relevant\_data} state variables
produced the \texttt{Failed} observation. Therefore, the
\texttt{Survey controller} will received this observation on its {\em
  external} \texttt{Sampling\_policy} which indicates that this state
varaiable is not managed anymore. At this point depending on this
reactor implementationm we have two possible outcomes:
\begin{enumerate}
\item \texttt{Survey  controller} model allows him to integrate this
  \texttt{Failed} observation. For example it can integarte that from
  now there's now way to take water samples. It is still able to
  navigate as \texttt{Pilot} is still available which allow him to
  continue this aspect of its current plan.
\item \texttt{Survey controller} models is not able to handle this
  unexpected failure resulting in turn on its failure to
  synchronize. This result on this reactor being also destroyed and
  the \texttt{Failed} observation is produced on the \texttt{survey}
  timeline.
\end{enumerate}
Even on the worst case scenario of the later case, we
note that a reactor failure only propagates up in the reactor graph. 
In our example, even if all the reactors that depends on
\texttt{Sampling} are entrained by its failure, we still keep the
three reactors \texttt{Vehicle}, \texttt{Pilot} and \texttt{Ship
  operation} allowing to  maintain the vehicle navigation control
(\texttt{Pilot}) along with high level safety operation 
(\texttt{Ship operation}). It illustrates how \rx can handle graceful
system degradation despite the failure of one or more reactors. It
also emphasize that it is critical to ensure that the low level
reactors are properly designed in order to be as robust as 
possible.

@@

\item Integrate the external state as provided by the owner of each
  external timeline into the plan database. 
  \begin{itemize}
  \item New observations are integrated by creating the
    corresponding token as a fact in the plan database
  \item If no observations have been received at this tick the last
    observation token restrict its \texttt{end} domaine to the
    interval $[\tau+1, +\infty)$
  \end{itemize}

@@

A key aspect of the \rx framework is interleaved plan and
execution. Both {\em synchronization} -- keeping track of execution --
and {\em deliberation} -- dealing with reactor planning -- of one
reactor are sharing the same {\em single} plan database which 
they modify alternatively as the \rx agent schedule their execution.

As noted above, it is synchronization which drives planning, so the
co-mingling between these two processes is critical to maintaining
state within a robot especially when it is immersed in a dynamic
environment. Further, it is important that \rx maintain
% A core aspect of this reactor is that it takes advantage of the
% specific sequencing enforced by the \rx architecture along with the
% fact that only 
one $plan$ structure shared between synchronization and planning. This
allows these two processes to not only be interleaved for agent
responsiveness, but ensures a viable mechanism to communicate.
